My title

### 2023-04-04 outputs/paper/paper.qmd
added abstract

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Huda Sahaf
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

>>>>

---
title: "My title"
subtitle: "My subtitle if needed"
author: 
  - Huda Sahaf
thanks: "Code and data are available at: LINK."
date: "`r Sys.time()`"
date-format: "D MMMM YYYY"
abstract: "This paper aims to investigate the history of racism in the beauty industry and how this impacts the inclusivity in the market. The complexions of models are assigned a lightness value and analyzed across 8 years. These results are compared to the foundation shade ranges across all major makeup brands across the U.S revealing a continuation of compounding racism within the industry as a whole."
format: pdf
number-sections: true
bibliography: references.bib
---
